% latex handlingsplan template v0.001, daniel
\documentclass[11pt]{article}
\usepackage[a4paper, total={7in, 9in}]{geometry}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage[usenames, dvipsnames]{color}
\definecolor{sdublue}{cmyk}{1.00,0.65,0.0,0.3}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{url}
\pagestyle{fancy}
\chead{\Large \textcolor{sdublue}{\bfseries\rmfamily Handlingsplan for kursus under Det Naturvidenskabelige Studienævn}}
\renewcommand{\headrulewidth}{0pt}
\cfoot{Page \thepage\ of \pageref{LastPage}}

\usepackage{tabu}

\newcommand{\TODO}[1]{\begingroup\color{red}#1\endgroup}
\newcommand{\answer}{\textcolor{red}{Please answer}}

\setlength\parindent{0pt}
\begin{document}
\tabulinesep=1.2mm
\begin{tabu} to 1.0\textwidth { | >{\mbox{}\color{sdublue}\bf}X[l] | X[2l] | } \hline
Kursuskode og navn &  DM562 --- Scientific Programming \\\hline
Semester {\normalfont (Efterår/forår og årstal)} & Efterår 2018 \\\hline
Undervisnings\-ansvarlig &  Marco Chiarandini (sammen med Luís Cruz-Filipe og Daniel Merkle) \\\hline
Øvrige undervisere &  Hans Kristian Anders Møller (instructor) \\\hline
Antal tilmeldte studerende til kurset & 13 in BlackBoard, 14 in the protocol \\\hline
Antal studerende, som har deltaget i evalueringen &  8  \hfill
Svarprocent:ca.~61\% \\\hline
På hvilke studieretninger og semestre indgår kurset &  The course is obligatory in the second year of Applied Mathematics \\\hline
Hvilken evalueringsform har været anvendt &  eletronic questionnaire \\\hline
Har der været foretaget en midtvejsevaluering på kurset? &  yes  \\ 
\hline
\end{tabu}

~\\[1cm]\textcolor{sdublue}{{\bf Beskriv evalueringens resultater} ---
  f.eks. indenfor:\\ {\small \em Kursets opbygning og placering,
    emner, undervisningsformer, fordeling af øvelsestimer,
    forelæsninger og e-timer mv, de studerendes arbejdsbelastning,
    undervisningsmaterialet, delprøver og forudsætningsprøver,
    sammenhæng med studiet, de enkelte læreres undervisning:}}



The course ran this year for the first time. It gives 10 ECTS and it
is made of two parts, a first part shared with DM550, Introduction to
Programming, taught by Luis, where students learn to program in java
and a second part, taught by Daniel and Marco, where students learn to
program in Python using Linear Algebra Applications.

The final pass/fail assessment was based on: a programming project from
the first part; and six small programming assignments from the second
part. The project was evaluated pass/fail, the assignments distributed a
score. In order to obtain a final pass assessment a student must have
passed the first project and collected 50\% of the available score in
the second part. The assignments were conducted through an submission
system that was providing automated grading on hourly basis with
possibility to resubmit until the deadline.

The students who passed the course in this way were 10. No student
registered for the reexam.

The course material for the second part is available at
\url{https://dm561.github.io/}.




\medskip

From the electronic questionnaire the following evaluation arises.

\begin{itemize}
\item Five students have spent in average less than 10 hours per week on
  this course while the remaining three have spent 11-15 hours.

\item The course is perceived as:

\begin{itemize}
\item  easy in comparison to others
\item  coherent with the study curriculum
\item matching the information available beforehand
\end{itemize}

\item The workload is considered at average level.

\item There is partial disagreement that the planning of the course was
  satisfactory. There is some criticism on the decision of working with
  two programming languages, Java and Python.

\item The second part of the course is perceived as:
 helpful to improve programming skills,
and to understand the importance of Linear Algebra.

\item The programming assignments in the second part of the course
  definitely motivated students in their study. The results provided on
  hourly basis were used to improve the code submitted.

\item All assignments of the second part were found relevant for the
  course (except by one respondent).

\item The open field for criticism to the three teachers was left almost
  empty indicating that the overall presence was satisfactory.
  
\item The instructor was evaluated positively under all aspects: level
  of knowledge, pedagogical competences, preparation, commitment.

\end{itemize}
  
~\\[1cm]\textcolor{sdublue}{{\bf Giver evalueringen anledning til justering af undervisning mv.}:\\
{\small \em Hvis ja, beskriv hvilke:}}

No, we plan no change.


~\\[1cm]\textcolor{sdublue}{{\bf Giver evalueringen anledning til ændring i kursusbeskrivelsen?}\\
{\small \em Hvis ja; beskriv hvilke:}}

No, we plan no change.

~\\[1cm]
\begin{tabu} to 1.0\textwidth { | >{\bf}X[3l] | >{\bf}X[l] | }
  \hline
  Behandlet af undervisningsudvalget på: & Dato:\\ & \\ & \\ \hline
\end{tabu}
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
