%\documentclass[a4paper,10pt]{report}
\documentclass[a4paper,10pt]{article}
%\pdfoutput=1
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage[a4paper,margin=2.5cm]{geometry}
%\usepackage{palatino}
\usepackage[math]{kurier}
%\usepackage[sc]{mathpazo} % consider options: osf, sc
\usepackage{xspace}
%\PassOptionsToPackage{latex2html}{hyperref}  
%\usepackage{html} 
\usepackage{url} 
%\usepackage{booktabs} 
%\usepackage{hyperref}
%\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{rotating}
%\usepackage{srctex}
\usepackage{color}
\usepackage{enumerate}
%\usepackage{afterpage}

\usepackage{arydshln}
\usepackage{etoolbox}
\usepackage{blkarray}
\usepackage{multirow}

\usepackage{listings}
\usepackage[vlined]{algorithm2e}


\usepackage{fancyvrb}
\RecustomVerbatimEnvironment{Verbatim}{Verbatim}{xleftmargin=5mm}

\graphicspath{{Figures/}}

\usepackage{physics}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{mylstset}
\usepackage{mystyle}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifshow
\showtrue
%\showfalse
\usepackage{exercises}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usepackage[all]{xy}


\newcommand{\row}[1]{
%HEVEA \begin{comment}
\ensuremath \overrightarrow{\mathbf #1}
%HEVEA \end{comment}
%HEVEA \overrightarrow{\mathbf #1}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{enumitem}
\newcommand{\lastwords}{End of Examination}
\newlist{subquestion}{enumerate}{1}
\setlist[subquestion,1]{label=(\alph*)}
\def\la{\langle}
\def\ra{\rangle}
\def\R{\mathbb R}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\setcounter{tocdepth}{1}




\title{%
\begin{flushleft}
DM561 -- Linear Algebra with Applications\\[0.3cm]
%{\Large Reexam for Obligatory Assignments, Autumn 2018} %
%\ahref{\url{http://www.imada.sdu.dk/~marco/DM559/Assignments-LA/sheet2.pdf}}{\tiny
%  [pdf format]}
%\\
\hrulefill
\\[-1.8cm]
\end{flushleft}
}


%\hrulefill \\[-1.8cm]
\author{}
\date{}


\begin{document}

\maketitle








\medskip

\begin{itemize}

\itemsep=1ex

\item The reexam consists of two separated assignments:

\begin{itemize}

\item \emph{Theory assignment}:
  \begin{itemize}
\item Specifications in this document
\item {\bf Deadline: Monday, March 25, 2019 at noon}
\item Hand in PDF via BlackBoard SDU Assignments.
  \end{itemize}
  
\item \emph{Applications assignment}:
  \begin{itemize}
  \item Specifications at the course web page
    \url{https://dm561.github.io/}:\\ assignments: asg1, asg2, asg3, asg4,
    asg5, asg6
  \item {\bf Deadline: Monday, April 1, 2019 at noon}
  \item Hand in via git push as during the course.
  \end{itemize}
\end{itemize}
  


\item You are expected to work individually on the assignments.

  
\item Deadline extensions will not be conceded.
\end{itemize}


\clearpage

\section*{Theory Assignment}


You may use the course book, the slides from the lecture, and notes from
the lectures and the exercises. You are allowed to use tools such as
Python or Maple to assist you in calculations, but you must write the calculations out
in full so that they can be followed by the examiners.  It is not
sufficient to present an answer, you must show how you found it.  If you
use a theorem from the book (or the slides), make a reference to
it. \newline
\vspace{5mm}

For questions, you may contact the lecturer by e-mail
\url{marco@imada.sdu.dk}. \\ You may answer in Danish or English. Your
solution must be handed in as a single PDF file clearly stating your
{\bf full name and birth date} on the front page. You have to hand in
using SDU Assignment before Monday, March 25 at noon.
%In case of
%irrecoverable technical problems with Blackboard, you may hand in the
%exam electronically by sending an email to the lecturer before the
%deadline. \\


% End title page


You may use the course book, the slides from the lectures, and notes from the lectures and exercises. 
It is not sufficient to give an answer, you must show how you found it. If you use a theorem from the book 
(or from the slides), make a reference to it. You may answer in Danish or English. Your solution must be 
uploaded to Blackboard as a single PDF file, clearly stating your {\bf full name and birth date} on the front page. 
You must submit the file using SDU Assignment. 




\newpage
\section*{Problem 1}
Consider the following system of linear equations in variables $x,y,z,w\in \R$.
\begin{align*}
x+2y&=0 \\
-2w+x&=4 \\
2z+2y&=-1 \\
4x+8y&=0
\end{align*}
\noindent
\begin{enumerate}
\item Write the augmented matrix of this system.
\item Reduce this matrix to row echelon form by performing a sequence of elementary row
operations.
\item Solve the system and write its general solution in parametric form.
\end{enumerate}


\section*{Problem 2}
Consider the following matrix
$$
M=\left[ \begin{array}{ccc} 1 & 0 & 1 \\ -1 & 1 & 0 \\ 2 & 2 & 2 \end{array} \right].
$$ \\
\noindent
\begin{enumerate}
\item Find $M^{-1}$ by performing row operations on the double
matrix $[M\; | \;I]$.
\item Is it possible to express $M$ as a product of elementary matrices? Explain why or why not.
\end{enumerate}



\section*{Problem 3}
Consider the following matrix
$$
M=\left[ \begin{array}{ccc} x_1 & x_2 & x_3 \\ x_4 & x_5 & x_6 \\ x_7 & x_8 & x_9  \end{array} \right]
$$ \\
with $x_i \in \R$ for all $i$ and $\det(M)=10$.
Let $N$ be given by
$$
N=\left[ \begin{array}{ccc} x_4 & x_5 & x_6 \\ x_1 & x_2 & x_3 \\ x_7+2x_1 & x_8+2x_2 & x_9+2x_3  \end{array} \right]
$$ \\
\begin{enumerate}
\item Find $\det(N)$.
\item Find $\det(N^2)$.
\end{enumerate}



\section*{Problem 4}
Let $P_1$ be the vector space consisting of polynomials of degree at most one with real coefficients with
the usual addition and scalar multiplication and with the inner product $\langle p,q\rangle=p(0)q(0)+p(1)q(1)$.
\begin{enumerate}
\item Let $T: P_1 \to P_1$ be a linear transformation with $\text{rank}(T)=1$.
Is $S$ an isomorphism?
\item Consider the two polynomials $f,g \in P_1$ with $f(x)=x+1$ and $g(x)=2x+\frac12$.
Do these form a basis for $P_1$? If so, is it an orthonormal basis?
\item Is it possible to find two orthogonal polynomials $f,g\in P_1$ and a scalar $t\in \R$ such that 
$t \cdot f=g$? Find such an $f$, $g$ and $t$ or show that it is not possible.
\end{enumerate}

\newpage

\section*{Problem 5}
Consider the linear transformation $T: \R^2 \rightarrow \R^2$ given by
$$
	T\left( \begin{array}{c} x \\ y \end{array} \right) = \left( \begin{array}{c} 0 \\ y-3x \end{array} \right)
$$
\begin{enumerate}
\item Find a basis for the kernel of $T$.
\item Find the rank and nullity of $T$.
\item Find the matrix of T with respect to the basis $B=\left\{ \left( \begin{array}{c} 2 \\ 2 \end{array} \right), \left( \begin{array}{c} 3 \\ 0 \end{array} \right)  \right\}$.
That is, find $[T]_{B}$.
\end{enumerate}

\section*{Problem 6}
Consider the following matrix
$$
A=\left[ \begin{array}{ccc} 2 & 1 & 0 \\ 0 & 0 & 0 \\ 0 & 3 & 2 \end{array} \right]
$$ \\
\begin{enumerate}
\item Find the eigenvalues for $A$.
\item For each eigenvalue, find a basis for the corresponding eigenspace.
\item Can you find matrices $P$ and $D$ such that such that $P^*AP=D$ with $D$ diagonal? Find $D$ and $P$ or argue that it is not possible.
\end{enumerate}


\begin{center}
\vspace{3cm}
--------- \textit{\lastwords} ---------
\end{center}


\label{finalpage}


\end{document}
