\documentclass[a4paper]{article}

\usepackage{geometry}
\geometry{paper=a4paper,twoside}
\geometry{top=18mm,bottom=27mm}
\geometry{inner=21mm,outer=17mm}

\usepackage[all]{xy}
\usepackage{comment}

\newcommand{\fit}{\mathsf{fit}}
\newcommand{\cost}{\mathsf{cost}}

\begin{document}

\begin{center}\LARGE\bf
  INTRODUCTION TO PROGRAMMING\\
  \Large DM536, DM562 (Fall 2018)\\ \medskip
  \large Second assignment -- Deadline: November 16th, 23h59\\
\end{center}

\section*{The traveling salesman problem}

Consider the following problem.
\begin{quote}
  A traveling salesman needs to visit $n$ cities, returning to the initial city at the end of his
  journey. In which order should he visit them in order to minimize the total distance he travels?
\end{quote}

This is a classical optimization problem, known as the \emph{Traveling Salesman Problem}. It has
numerous practical applications, such as:
\begin{itemize}
\item planning routes for product distribution;
\item optimizing resourse usage in factories;
\item designing flight routes;
\item analysing crystal structures.
\end{itemize}
The traveling salesman problem is also an example of an \emph{NP-complete} problem. From the
practical side, this means that there are no known polynomial algorithms to solve it (and most
computer scientists do not believe any such algorithms exist). Therefore, it is extremely useful to
develop fast algorithms that can be used in practice to find good solutions (although possibly not
the best ones).

\section*{Simulated annealing}

Simulated annealing is a technique for solving optimization problems that is inspired by the
chemical process of annealing materials such as glass or metal. In this methodology, we randomly
generate a potential solution, and then randomly change it. The amount by which we are allowed to
change the candidate solution is measured by a ``temperature'', which decreases as the number of
iterations increases. When mutations no longer produce better solutions, the process stops.

\section*{The project}

In this project we will apply simulated annealing to the traveling salesman problem. The parameters
of the problem are a list of $n$ cities and their geographical coordinates (two real numbers). The
distance between any two cities is defined as the Euclidean distance between their coordinates.

The candidate solution consists of a path that passes once through each city in the list, and
returns to the initial city. Each path $p$ has associated a cost $\cost(p)$, computed as the total
distance the salesman will travel if he follows path $p$.

There are two possible ways to mutate the solution.
\begin{description}
\item[Reversion.] The segment between two randomly chosen cities in the current path is reversed.
\item[Transport.] A segment between two randomly chosen cities in the current path is moved to
  another place in the path.
\end{description}

We start with the list of cities as candidate solution and an initial temperature $T$. At each
iteration, we randomly choose one of the two possible mutations. Next, we compute the difference $d$
in length between the original path and the new path. If this difference is negative (meaning that
the new path is shorter) we replace the solution by the new one. Otherwise, we generate a uniformly
distributed random number $r$ between $0$ and $1$ and replace the solution with the new one if
$e^{-d}/T > r$. If we try $N_{\mathrm{stop}}$ mutations without improving the solution, we stop and
return the current solution as the best one found. If we change our solution $N_{\mathrm{dec}}$
times at the current temperature, we update $T$ to $0.9\times T$.

The given class \verb!RandomUtils! provides methods for generating random numbers. Method
\verb!boolean coinFlip()! returns \verb!true! with probability $\frac12$ and \verb!false! with
probability $\frac12$. Method \verb!double getRandom()! returns a uniformly distributed random
number in the interval $[0,1]$. Method \verb!int getRandomValue(int n)! returns a uniformly
distributed value in the range $[0,n-1]$. Classes \verb!City! and \verb!CityGenerator! provide
methods for working with cities and initializing the list of cities.

\section*{Parameters and execution mode}


Your program should start by interactively requesting the parameters $T$, $N_{\mathrm{stop}}$ and
$N_{\mathrm{dec}}$ from the user.
On termination, it should print the final solution and its cost.

The simulation can be run in two modes:
\begin{enumerate}
\item in verbose mode;
\item in silent mode.
\end{enumerate}
In verbose mode, every time you update the solution you print the new path and its cost; every time
the temperature decreases, you also print out a message.
In silent mode, there are no messages during the simulation (but you still show the final result).

\section*{Expected results}

You must hand in a class \verb!Simulator.java! implementing the functionality described above.
Your class should run directly from the command line, and ask for any relevant input using only
command-line interaction.

You should also hand in a report describing the algorithm implemented, any design choices that you
think are important to document, and examples. The report will be the basis for the evaluation.

\section*{Suggestions}

It is recommended that you initially develop your program to run always in verbose mode.
Afterwards, you can add an interactive block to query the user for the desired mode, and extend your
code to report only if required.

\section*{Testing and examples}

Here are some example executions. Consider using the values given for the parameters. Then
experiment with your own set of cities and try to adjust the parameters to get the best results.

\subsection*{Example execution}
\begin{verbatim}
Enter 1 to use the default list of cities, or 2 to read a custom list from a file.
1
Initial temperature: 1000
Iterations until termination: 50
Iterations until temperature decreases: 100
Verbose mode (yes/no)? yes
New cost: A; B; C; J; K; L; M; D; E; F; G; H; I; N; O; cost: 98.61617427157424
New cost: A; B; C; J; K; L; M; D; E; F; G; H; N; I; O; cost: 97.59219951605684
New cost: A; J; C; B; K; L; M; D; E; F; G; H; N; I; O; cost: 97.28526709091133
New cost: A; J; C; B; K; L; M; D; G; F; E; H; N; I; O; cost: 92.16634050550802
New cost: A; J; C; B; K; L; D; M; G; F; E; H; N; I; O; cost: 91.19246989831531
New cost: N; I; O; A; J; C; B; K; L; D; M; G; F; E; H; cost: 91.1924698983153
New cost: N; I; O; A; J; C; B; K; M; L; D; G; F; E; H; cost: 90.56539153414928
New cost: N; A; J; C; B; I; O; K; M; L; D; G; F; E; H; cost: 89.37441862655926
New cost: N; A; J; C; B; I; O; G; D; L; M; K; F; E; H; cost: 83.94075312819918
New cost: N; A; J; C; B; I; O; G; D; L; M; E; K; F; H; cost: 83.87013744402356
New cost: N; A; O; I; B; C; J; G; D; L; M; E; K; F; H; cost: 83.5218336050916
New cost: N; A; O; I; B; C; J; D; G; L; M; E; K; F; H; cost: 79.82180427241855
New cost: N; A; J; C; B; I; O; D; G; L; M; E; K; F; H; cost: 77.00937212639572
Best path: N; A; J; C; B; I; O; D; G; L; M; E; K; F; H; cost: 77.00937212639572
\end{verbatim}

\subsection*{Example execution}
\begin{verbatim}
Enter 1 to use the default list of cities, or 2 to read a custom list from a file.
2
Please enter the file name:
cities
Initial temperature: 1000
Iterations until termination: 100
Iterations until temperature decreases: 50
Verbose mode (yes/no)? yes
New cost: A; B; C; D; E; H; I; J; F; G; K; L; M; N; O; cost: 101.81568180696138
New cost: A; B; C; I; J; F; G; K; D; E; H; L; M; N; O; cost: 101.16060716187265
New cost: A; B; C; I; J; K; G; F; D; E; H; L; M; N; O; cost: 100.93547427715662
New cost: A; B; C; I; J; E; H; K; G; F; D; L; M; N; O; cost: 97.8211254927697
New cost: A; B; C; I; J; E; H; K; G; L; D; F; M; N; O; cost: 93.6549995342063
New cost: A; B; C; I; J; E; H; F; K; G; L; D; M; N; O; cost: 84.87492087686945
New cost: A; B; C; I; O; N; M; D; L; G; K; F; H; E; J; cost: 83.54605127073576
New cost: B; A; C; I; O; N; M; D; L; G; K; F; H; E; J; cost: 83.47187272016998
New cost: B; A; C; I; O; N; M; D; E; H; F; K; G; L; J; cost: 81.78074855841416
New cost: B; C; A; I; O; N; M; D; E; H; F; K; G; L; J; cost: 77.72474105169442
New cost: B; C; A; I; O; N; D; E; H; F; K; G; L; M; J; cost: 76.24002320488822
New cost: B; C; A; I; O; N; D; L; G; K; F; H; E; M; J; cost: 73.18465741137734
New cost: B; C; A; I; O; N; D; L; G; K; F; E; H; M; J; cost: 72.86039650005222
New cost: B; C; A; I; O; N; D; L; G; K; M; F; E; H; J; cost: 72.77869416528992
New cost: B; C; A; I; O; N; D; L; G; K; M; E; F; H; J; cost: 70.37158143261439
New cost: B; C; A; I; O; N; D; H; F; E; M; K; G; L; J; cost: 70.02038633740273
New cost: B; J; C; A; I; O; N; D; H; F; E; M; K; G; L; cost: 68.37269723287774
New cost: C; J; B; A; I; O; N; D; H; F; E; M; K; G; L; cost: 67.80841438141378
Best path: C; J; B; A; I; O; N; D; H; F; E; M; K; G; L; cost: 67.80841438141378
\end{verbatim}

\subsection*{Example execution}
\begin{verbatim}
Enter 1 to use the default list of cities, or 2 to read a custom list from a file.
1
Initial temperature: 1000
Iterations until termination: 10
Iterations until temperature decreases: 25
Verbose mode (yes/no)? no
Best path: A; J; I; H; E; F; G; D; C; B; K; L; M; N; O; cost: 99.90270234212458
\end{verbatim}

\end{document}
